---
title: "Submission Template"
author: "<Your Name Here>"
date: "8/1/2021"
output: html_document
---

```{r setup, include=FALSE}
# We're using `require()` here because you will need these packages to run, test, and check against the baseline
require(stringr)
require(stringi)
require(testthat)
require(microbenchmark)
require(ggplot2)
knitr::opts_chunk$set(echo = TRUE)
```

## Session Info

Before we get started - let's make sure we know what tools you're working with

```{r sessionInfo}
sessionInfo
```
## Load in the test set and the solutions

The objects `text` and `solutions` will be used to test and check your work.

```{r test and solutions}
text <- c(
   "Pneumonoultramicroscopicsilicovolcanoconiosis is a really long word", 
   "It's a name that has been invented for a lung disease caused by breathing in very small pieces of ash or dust", 
   "Pneumono refers to the lung. Ultra means extremely, microscopic means tiny, silica is sand, volcano is self-evident, and coniosis is scarring.")

solutions <- c("Pneumonou-\nltramicro-\nscopicsil-\nicovolcan-\noconiosis\nis a\nreally\nlong word",
               "It's a\nname that\nhas been\ninvented\nfor a lung\ndisease\ncaused by\nbreathing\nin very\nsmall\npieces\nof ash or\ndust",
               "Pneumono\nrefers to\nthe lung.\nUltra\nmeans\nextremely,\nmicroscop-\nic means\ntiny,\nsilica\nis sand,\nvolcano\nis self-\nevident,\nand\nconiosis\nis\nscarring.")
```

## Establish the baseline within your environment

Everyone's machines will run at different speeds! So let's test the baseline in your environment so you can have a fair comparison.

```{r baseline}
base_bench <- microbenchmark::microbenchmark(
   str_wrap(rep(text, 1000), width=10),
   unit='s'
   )

microbenchmark:::autoplot.microbenchmark(base_bench) +
   ggplot2::theme_bw()
```

## Function template

Use this function template to submit your work. You're free to do whatever you want - but this template sets you up with the expectations laid out within the blog post.

```{r template}
overflow_wrap_solution <- function(text, width = 10) {
   
}
```

## Check your work

Before you check the performance, make sure that your function produces the correct results. You can use this chunk to evaluate

```{r check work}
testthat::test_that("All good!", {
   # Baseline
   base <- str_wrap(text, width=10)
   # Your solution
   check <- overflow_wrap_solution(text, width=10)
   # Evaluate
   testthat::expect_equal(base, check)
})
```

## Benchmark it!

Great - now you know your solution works. Let's benchmark and see how it performs.

```{r benchmark}
solution_bench <- microbenchmark::microbenchmark(
   overflow_wrap_solution(rep(text, 1000), width=10),
   unit='s'
   )

microbenchmark:::autoplot.microbenchmark(base_bench) +
   ggplot2::theme_bw()
```

And finally, let's look at how it compares to baseline. To keep it simple we're just going to use the mean. 

```{r compare}
summary(solution_bench)$mean - summary(base_bench)$mean
```

So - how'd you do? 
